\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-05-25 scratch/notes_john/JSS-article/JSS-article-3.Rmd
tweak draft JSS paper

We illustrate with an example adapted from a vignette in the \pkg{rsample} package, which uses the \code{attrition} data set from the \pkg{modeldata} package [@Kuhn:2024]. Here, with minimal explanation, is how one would perform LOO CV for this example using \pkg{rsample}:[^k-fold-used-in-rsample]
```{r rsample-example, cache=TRUE}
library(rsample)

>>>>

We illustrate with an example adapted from a vignette in the \pkg{rsample} package, which uses the \code{attrition} data set from the \pkg{modeldata} package [@Kuhn:2024] (and which is by a wide margin the most downloaded of the CV packages mentioned in the preceding paragraph). Here, with minimal explanation, is how one would perform LOO CV for this example using \pkg{rsample}:[^k-fold-used-in-rsample]
```{r rsample-example, cache=TRUE}
library(rsample)

### 2024-05-25 scratch/notes_john/JSS-article/JSS-article-3.tex
tweak draft JSS paper

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 891621
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.30934
bias-adjusted cross-validation criterion = 19.29207
95% CI for bias-adjusted CV criterion = (15.80161, 22.78253)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat) {
  if (!all(y %in% c(0, 1)))
    stop("response values not all 0 or 1")
  if (any(yhat < 0) ||
      any(yhat > 1))
    stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x1293c2ea8>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

@@

We illustrate with an example adapted from a vignette in the
\pkg{rsample} package, which uses the \code{attrition} data set from the
\pkg{modeldata} package \citep{Kuhn:2024}. Here, with minimal
explanation, is how one would perform LOO CV for this example using
\pkg{rsample}:\footnote{The example in the \pkg{rsample} vignette uses
  10-fold rather than LOO CV, but otherwise the code from the vignette
  is only trivially modified here.}

>>>>

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto, confint=TRUE)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 508110
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.23279
bias-adjusted cross-validation criterion = 19.21953
95% CI for bias-adjusted CV criterion = (15.76747, 22.67159)
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> BayesRule
\end{CodeInput}
\begin{CodeOutput}
function(y, yhat) {
  if (!all(y %in% c(0, 1)))
    stop("response values not all 0 or 1")
  if (any(yhat < 0) ||
      any(yhat > 1))
    stop("fitted values outside of interval [0, 1]")
  yhat <- round(yhat)
  result <- mean(y != yhat) # proportion in error
  attr(result, "casewise loss") <- "y != round(yhat)"
  result
}
<bytecode: 0x14aa65750>
<environment: namespace:cv>
\end{CodeOutput}
\end{CodeChunk}

@@

We illustrate with an example adapted from a vignette in the
\pkg{rsample} package, which uses the \code{attrition} data set from the
\pkg{modeldata} package \citep{Kuhn:2024} (and which is by a wide margin
the most downloaded of the CV packages mentioned in the preceding
paragraph). Here, with minimal explanation, is how one would perform LOO
CV for this example using \pkg{rsample}:\footnote{The example in the
  \pkg{rsample} vignette uses 10-fold rather than LOO CV, but otherwise
  the code from the vignette is only trivially modified here.}
